High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
LeNet implemented

function MLJFlux.build(b::LeNetBuilder, rng, n_in, n_out, n_channels)

@@

	front = Flux.Chain(
			   Conv((k, k), n_channels => c1, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Conv((k, k), c1 => c2, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Flux.flatten)
	d = Flux.outputsize(front, (n_in..., n_channels, 1)) |> first
    back = Flux.Chain(
        Dense(256, 120, relu),
        Dense(120, 84, relu),
        Dense(84, n_out),
    )
	return Flux.Chain(front, back)
end

# Final model:
lenet = ImageClassifier(
    builder=LeNetBuilder(5, 6, 16),
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)

# Convert to image:
function toimg(X)
    X = matrix(X) |> x -> reshape(x, 28, 28, :)
    X = coerce(X, GrayImage)
    return X
end

lenet = (X -> toimg(X)) |> lenet
```

@@

add_models = Dict(
    "Large Ensemble" => mlp_large_ens,
    "LeNet-5" => lenet,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble", 
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

>>>>

preproc(X) = reshape(X, (28, 28, 1, :))

function MLJFlux.build(b::LeNetBuilder, rng, n_in, n_out)

    _n_in = Int(sqrt(n_in))

@@

    preproc(x) = reshape(x, (_n_in, _n_in, 1, :))

	front = Flux.Chain(
        Conv((k, k), 1 => c1, pad=(p, p), relu),
        MaxPool((2, 2)),
        Conv((k, k), c1 => c2, pad=(p, p), relu),
        MaxPool((2, 2)),
        Flux.flatten
    )
	d = Flux.outputsize(front, (_n_in, _n_in, 1, 1)) |> first
    back = Flux.Chain(
        Dense(d, 120, relu),
        Dense(120, 84, relu),
        Dense(84, n_out),
    )

    chain = Flux.Chain(preproc, front, back)

	return chain
end

# Final model:
lenet = NeuralNetworkClassifier(
    builder=LeNetBuilder(5, 6, 16),
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)
```

@@

# LeNet-5 Ensemble:
lenet_ens = EnsembleModel(model=lenet, n=5)

add_models = Dict(
    "LeNet-5" => lenet,
    "LeNet-5 Ensemble" => lenet_ens,
    "Large Ensemble (n=50)" => mlp_large_ens,
)

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "LeNet-5 Ensemble",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```
